Supplementary Materials for Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-06-24 analysis/supplementary materials/Supplementary Materials.Rmd
Save supplementary figures outside of document

```{r, setup, echo = FALSE, message=FALSE}

library("Reproducibility.in.Plant.Pathology")
library("tidyverse")
library("pander")
library("report")
library("flextable")

@@

@@

@@

@@

@@

@@

>>>>

```{r, setup, echo = FALSE, message=FALSE, warning=FALSE}

library("Reproducibility.in.Plant.Pathology")
packages <- c(
  "tidyverse",
  "bayesplot",
  "bayestestR",
  "brms",
  "extrafont",
  "flextable",
  "ggpubr",
  "here",
  "knitr",
  "officer",
  "pander",
  "posterior",
  "report",
  "tools"
)

install.packages(setdiff(packages,
                         rownames(installed.packages())),
                 repos = "http://cran.us.r-project.org",
                 dependencies = TRUE)

invisible(lapply(packages,
                 library,
                 character.only = TRUE))

options(mc.cores = parallel::detectCores())
theme_set(theme_classic())

@@

```{r journal-code-test, echo=FALSE, message=FALSE, warning=FALSE}
p <- plot(equivalence_test(m_f1))

ggsave(
  filename = here(
    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_1.eps"
  ),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here(
    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_1.eps"
  ),
  outfile = here(
    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_1.eps"
  ),
  options = "-dEPSCrop"
)
include_graphics(path = here(
  "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_1.eps"
))
```

@@

```{r journal-data-test, echo=FALSE, message=FALSE, warning=FALSE}
p <- plot(equivalence_test(m_f2))

ggsave(
  filename = here(
    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_2.eps"
  ),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here(
    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_2.eps"
  ),
  outfile = here(
    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_2.eps"
  ),
  options = "-dEPSCrop"
)
include_graphics(path = here(
  "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_2.eps"
))
```

@@

```{r year-code-test, echo=FALSE, message=FALSE, warning=FALSE}
p <- plot(equivalence_test(m_g1))

ggsave(
  filename = here(
    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_3.eps"
  ),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here(
    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_3.eps"
  ),
  outfile = here(
    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_3.eps"
  ),
  options = "-dEPSCrop"
)
include_graphics(path = here(
  "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_3.eps"
))
```

@@

```{r year-data-test, echo=FALSE, message=FALSE, warning=FALSE}
p <- plot(equivalence_test(m_g2))

ggsave(
  filename = here(
    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_4.eps"
  ),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here(
    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_4.eps"
  ),
  outfile = here(
    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_4.eps"
  ),
  options = "-dEPSCrop"
)
include_graphics(path = here(
  "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_4.eps"
))
```

@@

```{r if5yr-code-test, echo=FALSE, message=FALSE, warning=FALSE}
p <- plot(equivalence_test(m_h1))

ggsave(
  filename = here(
    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_5.eps"
  ),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here(
    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_5.eps"
  ),
  outfile = here(
    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_5.eps"
  ),
  options = "-dEPSCrop"
)
include_graphics(path = here(
  "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_5.eps"
))
```

@@

```{r if5yr-data-test, echo=FALSE, message=FALSE, warning=FALSE}
p <- plot(equivalence_test(m_h2))

ggsave(
  filename = here(
    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_6.eps"
  ),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here(
    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_6.eps"
  ),
  outfile = here(
    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_6.eps"
  ),
  options = "-dEPSCrop"
)
include_graphics(path = here(
  "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_6.eps"
))
```
